Presentation

### 2023-04-16 Presentation.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

--- 
plots
- plot of citations by race over time
- plot of frequency of citation versus hour in day
- mph over speed limit by year

---
plot

```{r}
#source("plots/plot.r", local = TRUE, print.eval = TRUE)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("shiny_plot_setup.R", echo=FALSE)
#show_col_types = FALSE
```

@@

- plot of citations by race over time  
- plot of frequency of citation versus hour in day  
- mph over speed limit by year

## Pyramid 
```{r, message = FALSE}
source("subscripts/citation_pyramid.R", local = TRUE, print.eval = FALSE, echo= FALSE, verbose= FALSE)
pyramid_cites()
```

## Violin
```{r, message = FALSE}
source("subscripts/violin_speed.R")
violin_speed()
```

@@

#Race Line Graph by Year: line_ry()
#waffle plot: waffle()
